Supplementary Materials for 'Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-05 analysis/supplementary materials/supplementary materials.Rmd
Delete unnecessary spaces
Try loading this library to knit supplementary materials

```{r, setup, echo = FALSE, message=FALSE, warning=FALSE}

@@

install.packages(setdiff(packages,
                         rownames(installed.packages())),
                 repos = "http://cran.us.r-project.org",
                 dependencies = TRUE)

invisible(lapply(packages,
                 library,
                 character.only = TRUE))

options(mc.cores = parallel::detectCores())
theme_set(theme_classic())

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  dev = "cairo_ps"
)

@@

>>>>

```{r, setup, echo=FALSE, message=FALSE, warning=FALSE}

@@

# install packages if needed
install.packages(setdiff(packages,
                         rownames(installed.packages())),
                 repos = "http://cran.us.r-project.org",
                 dependencies = TRUE)

# load packages for use in knitting Rmd
invisible(lapply(packages,
                 library,
                 character.only = TRUE))

library("Reproducibility.in.Plant.Pathology")

@@

opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  out.width = "100%",
  comment = "#>",
  dev = "cairo_ps",
  cache = FALSE
)

theme_set(theme_classic())
